Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-26 5-Analysis.tex

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). This follows the way the challenge is presented and this organisation allows for the possibility of easy extensions.

>>>>

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). As the figure shows the VirtualModels play the role of metamodels, in the sens of concept definition with a level blind approach. The VirtualModel instance plays the role of instance of metamodels with no 
This follows the way the challenge is presented and this organisation allows for the possibility of easy extensions.
